Proposal: Loose Grammar Inference for Lossy Compression

### 2012-10-18 proposal.tex
Authoring lossy compression background and resources sections

@@

\subsection{Implementation and Resources}

>>>>

While we were unable to find work in the area of lossy grammar compression, a
number of existing techniques for lossy hierarchical compression more broadly
may be applicable.  Kieffer notes that lossless hierarchical compression
methods, including context-free grammars, can be used interchangeably to
equivalently represent the structure of a given input \cite{tutorial}.
However, we found no such claims for lossy hierarchical compression methods.

Kieffer briefly identifies two primary methods for lossy hierarchical
compression: wavelet-based and fractal-based schemes \cite{tutorial}.  In
wavelet-based schemas, a signal is compressed by recording the largest
coefficients of its wavelet decomposition, given a suitable wavelet function.
Clustered coefficients can be stored in a compact form and used to encode
hierarchical structure.  The JPEG image format uses a similar technique in
order to compress images lossily \cite{jpeg}.

In fractal compression, we wish to determine a set of contraction maps $w_i$
over the domain of the data such that the fixed point of the $W(B) = \bigcup
w_i(B)$ is the data set itself.  In this way, this fractal transform captures
the self-similarity of an input by equating it with a covering of contractions
of itself.  By restricting $w_i$ in, say, image compression, to affine
transformations, we can easily represent each contraction map by a small
sequence of coefficients.  Barnsley describes how to ``home in'' on the right
coefficients to approximately represent a given input.  Interestingly, fractal
compression on images can sometimes produce results which appear to be of much
higher resolution than the original, which suggests that the technique provides
some great measure of insight into the data's structure.

Witten, \emph{et.\ al.}\ apply fractal compression to the area of text
compression in order to generate texts which approximate a given input.  This
yields a extraordinarily high compression ratio at the expense of time.  The
authors do not supply their algorithm for fractal-based generation, but suggest
that their particular algorithm may only be applicable to a certain style of
prosaic text.

Work has also been done regarding the lossy compression of particular input
formats.  For text, methods such as replacing words with synonyms
\cite{semanticlossy} or reordering the middle letters of a word (i.e., all
letters save for the first and last) \cite{semilossless} have been explored.
Applying such methods before transforming text into a grammar might yield
interesting structural results, although we suspect that, as non-hierarchical
schemes, they may not.

We will try to adapt this variety of lossy compression techniques to function
at the different points in the process of converting data into the form of a
compressed grammar.

@@

\subsection{Resources}

The primary resources we will require is source code or a functioning binary
for the existing lossy compression, grammar transformation, and grammar
compression algorithms we wish to use for our overall lossy grammar compression
scheme.
